\section{Data}
\label{DataSets}
Our dataset is a combination of four datasets collected from Eurostat\footnote{epp.eurostat.ec.europa.eu/portal/page/portal/statistics/search\_database}. These datasets contain data from thirty or more years back. We combined the datasets based on year and name of the nation using a self-written algorithm. 

Eurostat gives multiple options when extracting datasets from their databases. We chose data from the European nations in the years 1983-2012.

The four datasets (and their identifiers in the database) are:
\begin{my_description}
\item[Unemployment rate] Database identifier: "une\_rt\_a"\footnote{Selected values in extraction: S\_ADJ="Not seasonally adjusted data"; Age = "Total"; Sex="Total".}
\item[Balance of payments]Database identifier: "bop\_q\_c"\footnote{Selected values in extraction: Currency= Million Euro; Post = Current account; Flow = "Net"; Partner="All countries of the world".}
\item[GDP per inhabitant]Database identifier: "nama\_gdp\_c"\footnote{Selected values in extraction: Unit="Euro per inhabitant"; Indic\_NA="Gross domestic product at market prices".}
\item[Population]Database identifier: "demo\_pjan"\footnote{Selected values in extraction: Age="Total"; Sex="Total";}
\end{my_description}

We consider Eurostat to be a reliable source of data, as Eurostat is a part of the European Commission. Its main responsibilities are to provide statistical information to the institutions of the European Union and to promote harmonisation of statistical methods across the member states. The data and statistics are provided by the members of the European Union and is available free of charge from the Eurostat website.

As some nations may not have had data available or been part of the European Union in the 80s and 90s, Eurostat have some missing values in the dataset. The dataset is quite clean except for this missing data.
